Practical Optional Types for Clojure

### 2015-07-11 formal-model.tex
some typos, submitted

We describe the other \updateliteral{} cases.
The first \classpe{} case updates
to \class{} if \classconst{} returns \Value{\class{}}.
The second \keype{\k{}} case detects contradictions in absent
keys. % not overlapping with \Nil{}.
The third \keype{\k{}} case updates unknown entries to be mapped to \Nil{} or absent.
The fourth \keype{\k{}} case updates unknown entries to be \emph{present}
when they do no overlap with \Nil{}.

>>>>

We describe the other \updateliteral{} cases.
The first \classpe{} case updates
to \class{} if \classconst{} returns \Value{\class{}}.
The second \keype{\k{}} case detects contradictions in absent
keys. % not overlapping with \Nil{}.
The third \keype{\k{}} case updates unknown entries to be mapped to \t{} or absent.
The fourth \keype{\k{}} case updates unknown entries to be \emph{present}
when they do not overlap with \Nil{}.
